---
title: "British Airways"
output: html_notebook
---
```{r}
# loading related packages
library(moments)
library(Amelia)
library(dplyr)
library(psych)
library(purrr)
library(tidyr)
library(ggplot2)
library(caret)
library(GGally)
library(corrplot)
library(plotly)
library(rpart)
library(rpart.plot)
```

```{r}
data <- read.csv("customer_booking.csv")
```

```{r}
View(data)
```

```{r}
summary(data)
```

Studying the dataset
```{r}
# checking variable type
table(data$flight_day)
table(data$trip_type)
table(data$sales_channel)
table(data$route)
table(data$booking_origin)
```

The data types looks good as per the summary statistics.
The data includes 7 days of a week.
Customers use 2 channels: Internet, Mobile.
There are 3 types of trips: Circle trip, one way, and round trip.

```{r}
# understanding data distribution
hist(data$num_passengers, col="blue")
hist(data$purchase_lead, col="blue")
hist(data$length_of_stay, col="blue")
hist(data$flight_hour, col="blue")
hist(data$flight_duration, col="blue")
```

num_passengers, purchase_lead, and length_of_stay are skewed to the right.
flight_hour is normally distributed
flight_duration is skewed to the left

```{r}
table(data$wants_extra_baggage)
table(data$wants_preferred_seat)
table(data$wants_in_flight_meals)
table(data$booking_complete)
```

```{r}
#checking for missing values
missmap(data, col= c("blue", "grey"), y.at=1, y.labels = '', legend = TRUE)
```
It is visible that the dataset doesn't have missing values. We would have to handle the missing values before creating a predictive model.

```{r}
# transforming skewed data
# num_passengers
trans_num_passengers <- log(data$num_passengers)
par(mfrow=c(1,2))
hist(data$num_passengers, c="blue", main = "Original")
hist(trans_num_passengers, c= "blue", main = "Transformed")

```

```{r}
# purchase_lead
trans_purchase_lead <- log(data$purchase_lead)
par(mfrow=c(1,2))
hist(data$purchase_lead, c="blue", main = "Original")
hist(trans_purchase_lead, c= "blue", main = "Transformed")

```

```{r}
# length_of_stay
trans_length_of_stay <- log(data$length_of_stay)
par(mfrow=c(1,2))
hist(data$length_of_stay, c="blue", main = "Original")
hist(trans_length_of_stay, c= "blue", main = "Transformed")

```

To transform the left skewed variable flight_duration, I will use square root transformation.

```{r}
trans_flight_duration <- sqrt(data$flight_duration)
par(mfrow=c(1,2))
hist(data$flight_duration, c="blue", main = "Original")
hist(trans_flight_duration, c= "blue", main = "Transformed")
```

Now, I need to change data types of 'character' variables into 'numerical' variables. Because, predictive models require all variables to be numeric.
variables need to be changed: sales_channel, trip_type, flight_day, route, booking_origin.

```{r}
data$sales_channel <- factor(data$sales_channel, levels = c('Internet', 'Mobile'))
data$sales_channel <- as.numeric(data$sales_channel)
class(data$sales_channel)
```

```{r}
# trip_type
data$trip_type <- factor(data$trip_type, levels = c('CircleTrip', 'OneWay', 'RoundTrip'))
data$trip_type <- as.numeric(data$trip_type)
class(data$trip_type)
```

```{r}
# flight_day
data$flight_day <- factor(data$flight_day, 
                          levels = c('Fri', 'Sat', 'Sun', 'Mon', 'Tue', 'Wed', 'Thu'),
                          labels = c(1,2,3,4,5,6,7))

data$flight_day <- as.numeric(data$flight_day)
class(data$flight_day)
```
I will use label-encoding to transform 'route'

```{r}
data$route <- as.numeric(factor(data$route))
data$booking_origin <- as.numeric(factor(data$booking_origin))
```


```{r}
class(data$route)
class(data$booking_origin)
```
I will check if we got any missing value in the transformation process.
```{r}
missmap(data, col = c("blue", "grey"), y.at = 1, y.labels = '', legend = TRUE)
```

There's none. So, the dataset is ready for creating predictive model.
I will check correlation between the variables.

```{r}
ggcorr(data, label = TRUE)
```
None of the variables have very high positive or negative correlation. Their correlation range between 0 to 0.3 which is quite low.

I will build a linear model.

```{r}
sample_size <- floor(2/3 * nrow(data))
set.seed(3)
data <- data[sample(nrow(data)), ]
data.train <- data[1:sample_size, ]
data.test <- data[(sample_size+1) : nrow(data), ]

formula = booking_complete~.
```

```{r}
linearmodel <- lm(formula = formula, data = data)
summary(linearmodel)$coefficients
```

```{r}
as.formula(
  paste0("y ~ ", round(coefficients(linearmodel)[1], 2), "+",
         paste(sprintf("%.2f * .%s", coefficients(linearmodel)[-1],
                       names(coefficients(linearmodel)[-1])),
               collapse = "+")
         )
)
```
From the formula it can be interpreted that num_passengers, purchase_lead, length_of_stay, flight_hour, flight_day, route, booking_origin do not have any influence on predicting the target variable booking_completion.
A change is trip_type, wants_extra_baggage, wants_preferred_seat, and wants_ins_flight_meal can increase the target variable.
On the other hand, a change in sales_channel and flight_duration can decrease the target variable.

The values are quite low. It is difficult to make a decision based on this model.
So, I am going to use another model to assess the dataset.

```{r}
library(randomForest)
```

```{r}
data$booking_complete <- as.factor(data$booking_complete)

x <- data[, -which(names(data) == "booking_complete")]
y <- data$booking_complete

rf_model <- randomForest(x, y)

importance <- rf_model$importance

print(importance)
```
The result indicates that purchase_lead, flight_hour, route, length_of_stay, flight_day are the most important predictors for determining booking_complete, as these variables have high MeanDecreaseGini values.
It also suggests that variables related to booking lead time and booking origin are more important than other factors.
This model is giving a better idea of customer behavior pattern and can be used for decision making.
It is important to choose the right model for a particular dataset, sicne this can highly impact decision making process.

creating visualisation

```{r}
varImpPlot(rf_model, main = "Variable Importance Plot")
```

