---
title: "BUS5DWR Assignment 2"
output: html_notebook
---

Q 1.1::
```{r}
library(dplyr)
library(tidyverse)

# loading datasets
show <- read.csv("show.csv")
MaturityType <- read.csv("MaturityType.csv")

#Renaming columns to remove space
colname <- names(show)
colname
names(show) <- str_replace_all(colname, "\\.", "")
colname

# Checking datatypes and changing data type of Date column
str(show)
show$DateAdded <- as.Date(show$DateAdded,"%d/%m/%y")

# Showing a summary of each dataframe
summary(show)
summary(MaturityType)
```
Q 1.2::
```{r}
# Checking if there are any duplicate rows
carry_duplicate_data <- any(duplicated(show))
carry_duplicate_data

# Checking which rows are duplicate
duplicate_row <- which(duplicated(show))
duplicate_row

# Showing duplicate data
duplicate_show <- subset(show, duplicated(show))
duplicate_show

# Removing duplicates
show <- unique(show)
show

# Modifying ImdbScore column
show$ImdbScore <- as.numeric(gsub("/10", "", show$ImdbScore))
str(show)
```
Q 1.3::
```{r}
# chosen production country = South Korea, chosen year = 2020

# Joining two dataframes
show_maturity <- full_join(show, MaturityType, c("Rating" = "Maturity.Type"))

# Displaying TV Shows for mature audience
matureAudience <- filter(show_maturity, ProductionCountry=="South Korea", ReleaseDate == 2020, Rating == "TV-MA", ContentType == "TV Show",  )
matureAudience
```

Q 1.4::
```{r}
# Displaying titles with "teen" and "high school"
teenhighschool <- show %>%
  filter(str_detect(show$Description, "teen", negate = FALSE), str_detect(show$Description, "high school", negate = FALSE)) %>%
  select(Title, ReleaseDate, ImdbScore) %>%
  arrange(ReleaseDate, desc(ImdbScore)) %>%
  head(5)
teenhighschool
```
Q 1.5::
```{r}
# Displaying TV Shows for general audience
generalAudience <- show_maturity %>% 
  filter(Rating == "TV-G", ContentType == "TV Show") %>%
  group_by(ProductionCountry) %>%
  summarise(NumberOfTVShows = n(), AvegareScore = mean(ImdbScore, na.rm = TRUE)) %>%
  arrange(desc(NumberOfTVShows)) %>%
  head(3)
generalAudience
```

Q 1.6::
```{r}
library(ggplot2)

# Drawing a boxplot
show %>%
  filter(ProductionCountry %in% c('United States', 'Canada'), ReleaseDate > 2010) %>%
  ggplot() +
  aes(x = ProductionCountry, y = ImdbScore) +
  geom_boxplot() +
  xlab('Production Country') + ylab('Imdb Score') +
  ggtitle('Imdb Score Distribution In United States and Canada')

# five values of United States
library(stats)

fiveValues_us<- (boxplot.stats(show[show$ProductionCountry == 'United States',]$ImdbScore))
fiveValues_us

#five values of Canada
fiveValues_canada<- (boxplot.stats(show[show$ProductionCountry == 'Canada',]$ImdbScore))
fiveValues_canada
```
Insights: From the five values of United States's boxplot, it is visible that the minimum Imdb score is 3.7, the first quartile (Q1) is 5.9 which mean 25% data falls below 5.9, median is 6.7, the third quartile (Q3) is 7.4 which means 75% data falls below 7.4, and the maximum Imdb score is 9.4. 
From the five values of Canada's boxplot, it is visible that the minimum Imdb score is 3.50, the first quartile (Q1) is 5.45 which mean 25% data falls below 5.45, median is 6.50, the third quartile (Q3) is 7.35 which means 75% data falls below 7.35, and the maximum Imdb score is 8.70.
In conclusion, there are only slight differences between the score distributions of the two countries and United States has comparatively higher scores than Canada.

Q 1.7a::
A mother can choose a good movie for her children by seeing the ratings of the movies. For a child who is less than 7 years old TV-Y and G rated movies would be most suitable.

Q 1.7b::
```{r}
# Displaying top 5 movies
movies_for_children_under_7 <- show_maturity %>%
  filter(ContentType == 'Movie', Rating == 'G' | Rating == 'TV-Y') %>%
  arrange(desc(ImdbScore)) %>%
  head(5)
movies_for_children_under_7
```
Q 1.7c::
Insights and recommendations: In movies_for_children_under_7 top 5 movies are ranked based on their Imdb score. All the movies are rated TV-Y, TV show designed to be appropriate for all children, and G, Suitable for general audience. Mothers can choose these movies for their children who are below 7 years old.


Q 2.1::
```{r}
install.packages("readxl")
library(readxl)

# loading dataset production
production <- read_excel("Production.xlsx", skip = 2, col_names = FALSE, range = "A3:F204")
colnames(production) <- as.character(unlist(production[1,]))
production <- production[-1,]

View(production)

# Renaming columns to remove 'Year'
production <- production %>%
  rename("2017" = "Year 2017", "2018" = "Year 2018", "2019" = "Year 2019", "2020" = "Year 2020", "2021" = "Year 2021")

glimpse(production)
```

Q 2.2a::
```{r}
# Transforming dataframe into three columns
production <- production %>%
  pivot_longer(c(2:6), names_to = "Year", values_to = "Average Rating", values_drop_na = TRUE)
```
Q 2.2b::
```{r}
# Spliting the first column
production <- production %>%
  separate(`Production Country / Maturity Type`, c("ProductionCountry", "MaturityType"), sep = "/")

```
Q 2.2c::
```{r}
# Spliting column 'Average Rating'
production <- production %>%
  separate(`Average Rating`, c("NumProducts", "Score"), sep = "-")

# Checking data types
str(production)

# Changing data types
production$NumProducts <- as.numeric(production$NumProducts)
production$Score <- as.numeric(gsub("/10", "", production$Score))
```
Q 2.2d::
```{r}
# Displaying the number of columns and rows
dim(production)
```
Q 2.2e::
```{r}
# Number of distinct countries
distinct_countries <- production %>%
  distinct(ProductionCountry) %>% n_distinct()
cat("Number of distinct countries:", distinct_countries, "\n")

# Number of distinct years
distinct_years <- production %>%
  distinct(Year) %>% n_distinct()
cat("Number of distinct years:", distinct_years, "\n")
```
Q 2.3::
```{r}
# Displaying countries with average score between 6.8 to 7.0
score_between_6.8to7 <- production %>%
  filter(Year == 2021 & between(Score, 6.8, 7.0))
score_between_6.8to7
country_list <- unique(score_between_6.8to7$ProductionCountry)
cat("Countries that have an average score from 6.8 to 7.0 in 2021:", country_list, "/n" )
```
Q 2.4::
```{r}
# Loading dataset
continent <- read_excel("Production.xlsx", sheet = "Continent", skip = 2, col_names = FALSE, range = "A3:B252")
colnames(continent) <- as.character(unlist(continent[1,]))
continent <- continent[-1,]

View(continent)

# Renaming columns
continent <- continent %>%
  rename("Country" = `Country or Area`, "Continent" = `Continent Name`)

# Calculating number of countries
num_of_countries <- continent %>%
  distinct(Country) %>% n_distinct()
cat("Number of total countries:", num_of_countries, "\n")

# Trimming space after country name in Production dataset
production$ProductionCountry <- trimws(production$ProductionCountry, "right")

# Cleaning continent dataset
continent <- continent %>%
  mutate(Country = case_when(
    Country == "China, Hong Kong Special Administrative Region" ~ "Hong Kong",
    Country == "Russian Federation" ~ "Russia",
    Country == "United Kingdom of Great Britain and Northern Ireland" ~ "United Kingdom",
    Country == "United States of America" ~ "United States",
    Country == "Viet Nam" ~ "Vietnam",
    TRUE ~ as.character(Country)
  ))

# Countries that do not appear in the data worksheet
countriesNotInDataSheet <- anti_join(continent, production, c("Country" = "ProductionCountry"))
cat("Number of countries that do not appear in the data worksheet:", nrow(countriesNotInDataSheet), "\n")
```

Q 2.5a::
Proposed criteria: The most effective way to identify Asian countries which Netflix should target to further grow their market is to analyse the countries based on their score. If we look at scores of only one year that will not give a overall scenario. So, we need to calculate their average score over 5 years and rank countries based on that. Through this we can identify countries that have a growing market.

Q 2.5b::
```{r}
# Joining datasets
production_continent <- left_join(production, continent, c("ProductionCountry" = "Country"))
View(production_continent)

# Displaying top 5 countries based on proposed ranking
top5AsianCountries <- production_continent %>%
  filter(Continent == "Asia") %>%
  group_by(ProductionCountry) %>%
  summarise(Average_Score = mean(Score)) %>%
  arrange(desc(Average_Score)) %>%
  head(5)
top5AsianCountries
```
Q 2.5c::
```{r}
# Drawing a bar chart
ggplot(top5AsianCountries, aes(x = ProductionCountry, y = Average_Score)) +
  geom_bar(stat = "identity", fill = "blue") +
  ggtitle("Top 5 Asian Countries by Score ") +
  xlab("Country") +
  ylab("Average Score") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```
Q 2.5d::
Insights: In top5AsianCountries it is visible that the top 5 countries with the highest average score are Israel, Lebanon, Japan, Bangladesh, and China. Israel has the highest average score of 7.54, Lebanon has 7.13, Japan and Bangladesh have scores of 6.9 and China's score is 6.8. These scores are depicting a growing market in these regions. So, to expand it's market Netflix should develop strategies on enhancing customer base in these countries.
